Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-30 raspi_journal.tex
Added Simon Wunderlich as author

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universi\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, frank.fitzek\}@tu-dresden.de}

>>>>

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3}$, Simon Wunderlich $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Daniel Lucani and Frank Fitzek}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de}
